# Deconvolution report

__Started on__

```{r start, echo=FALSE}
timestamp()
.START <- Sys.time()
``` 

# Initalisation
```{r setup, include=FALSE}
library(knitr)
hook2 <- function(x){ gsub("```\n+```\n", "", x) }
knit_hooks$set(document = hook2)
```

```{r load_lib}
library(CellMix, quietly = TRUE)
```

# Data

Type: ``{r} class(eset)``
```{r, data_show}
eset
```

## Identify annotation package
The process stops if the GPL cannot be mapped to a Bioconductor annotation package.
```{r annotation, echo=2}
ann <- annotation(eset)
annotation(eset) <- biocannotation(eset)
if( annotation(eset) == '' ){
	stop("Could not map platform '", ann, "' to a Bioconductor annotation package")
}
```

## Overview

```{r data_overview, echo=FALSE}
# expression object
eset
# plot densities
library(affy)
plotDensity(exprs(eset))
```
### Sample groups
```{r data_summary}
# disease groups [reorder levels: use NORMAL as baseline]
groups <- eset$disease
groups <- relevel(groups, 'NORMAL')
# show cross tissue
table(groups, eset$tissue)
```

# Deconvolution

## Estimate cell proportions
Method: Abbas signatures + lsfit

```{r deconv_p, eval=FALSE}
resP <- gedBlood(eset, method='lsfit', verbose = TRUE)

# plot estimated proportions
propplot(resP)
```

To avoid sample size issue, we deconvolve at the CBC level:
```{r asCBC}
# aggregate as CBC
resCBC <- asCBC(resP)
propplot(resCBC)
```

## Estimate cell-specific expression
Method: `r args$method`

```{r deconv_cs, eval=FALSE}
resCS <- ged(eset, coef(resCBC), data = groups, method = args$method, verbose = TRUE, nperms = 10)
```

## Save result

### R binary files
```{r results_save}
save(resP, resCBC, resCS, file=paste0(ACCESSION, '_cs.RData'))
```

### Database
```{r results_db}
# TODO
```

# Benchmark against known data
## Proportions
```{r benchmark_p, eval=FALSE, echo=2:3}
if( hasCoef(eset) ){
	# correlations
	profplot(eset, res)
}else cat("SKIP: no reference proportions are available.\n")
```

## Cell-specific signatures
if( hasBasis(eset) ){
	# correlations
	profplot(t(basis(eset)), t(basis(res)))
	# AUCs
}else cat("SKIP: no reference cell-specific signatures are available.\n")
```

__Finished on__

```{r done, echo=FALSE}
timestamp()
.END <- Sys.time()
cat("Total elapsed time - ", capture.output(show(.END - .START)), "\n")
```
